---
title: '[MACAQUE] rs-fMRI DREADS HoDo'
author: "E Procyk"
date: "20/06/2023"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library('plotrix')
library('plot.matrix')
library(corrplot)
library(ggplot2)
library(psych)
library(RColorBrewer)
library(gplots)
library(reshape2)
library(MASS)
#library("ppcor")
library(plyr)
library(dplyr)
library(Rmisc)
library("stats")
library("lsmeans")
library(multcompView)
library(multcomp)
library(lme4)
library(lmerTest)
library(pbkrtest)
library(forcats)
#library('fmsb') 
#library('ggradar')
library('dbplyr')
library('emmeans')
#library("ggnewscale")
#library("report")
library(rstatix)
#function

#recode number to character in the list = create a function call recode2
recode2 <- function ( data, fields, recodes ) {
  for ( i in which(names(data) %in% fields) ) { # iterate over column indexes that are present in the passed dataframe that are also included in the fields list
    data[,i] <- car::recode( data[,i], recodes)
  }
  data
}


regenerate = FALSE


pathout <- "C://Users/E Procyk/Dropbox/Main_drop/R/MRI/CMAs_RSN/CMAr DREADDs/DREADDPath/"
session_type <- read.table(paste0(pathout,"DCZInjectionSchedule.txt"), header=TRUE)

session_type$period <- as.factor(session_type$period)
session_type$monkey <- as.factor(session_type$monkey)
session_type$injection <- as.factor(session_type$injection)
session_type$session <- as.factor(session_type$session)

```

## ABOUT:
This is reorganized from Camille Giacometti's script used for the RSN study with TUS

[[ this pdf document display the generated plots for the following:

Data are acquired on 3T MRI in anaesthetized macaque monkeys (n=5, 1M, 4F). Data are splitted in a SHAM condition (no stimulation) and a TUS AMG condition (transcranial ultrason stimulation of the bilateral amygdala). SHAM condition is composed by 1 single run and TUS condition by 2 runs. Each of the runs in each conditions is also separated in 6 differents group of volumes (=TR) size by sequence of 400: 400TR, 800TR, 1200TR, 1600TR, 2000TR and 2400TR (note that CELIA SHAM Session LOKI TUSAMG Session RUN2 have a total on 2000 TR only). 

The functional connectivity (i.e. correlation strength) pattern at rest between **4 AMYGDALA main nuclei (LA, BL, BM and Ce)** and **16 medial Prefrontal cortex ROIs (Area25,SROSp, SROSm, SROSa, Fork32, CgS11, CgS10, CgS9, CgS8, CgS7, CgS6, CgS5, CgS4, CgS3, CgS2, CgS1)** was assed for each of the different conditions, runs, volumes and hemisphere. ]]



```{r warning=FALSE, message = FALSE, include=FALSE}


# load CHAMR atlas key
CHARM <- read.table('E:/DREADDS/CHARM-SARM_ATLAS_SPACE/CHARM_ATLAS/CHARM_key_6.txt', header=TRUE)
CHARM <- CHARM[-c(79, 80,81, 82, 83, 86), ]

#set up environnement and folder
path <- 'E:/DREADDS/CHARM-SARM_ATLAS_SPACE/' 

# monkey list c('HOMER','DONUT','KATE', 'OSCAR','POPEYE','YURI','LOKI','NALA')
mkey <- c('HOMER','DONUT')

hemisph <- c('LH','RH')

sessionMax <- 8

# this step is to load 1D files and put them into matrix txt files that then will connect with Camille's script
#if (regenerate){
  
 if (regenerate){
  
  for (mk in 1:length(mkey)){

    for (session in 1:sessionMax){
      for (hem in 1:2){
        
        #Folder and path 
          setwd(paste0("E://DREADDS/CHARM-SARM_ATLAS_SPACE/",mkey[mk],"/",mkey[mk],"_",session,"/CHARM_ATLAS_ROI/",hemisph[hem]))
          folder2 = paste0("E:/DREADDS/CHARM-SARM_ATLAS_SPACE/",mkey[mk],"/",mkey[mk],"_",session,"/CHARM_ATLAS_ROI/",hemisph[hem])
       
          for (ran in 1:5){ # will import 1D files and turn into matrix, save in .txt file
          
        #import files for 1 monkey, 1 run, 1 hemisphere and rename variables
          filelist <- list.files(path=folder2, pattern=paste0("RUN",ran), full.names = F) 
          filelist <- as.list(filelist)
          dataLH <- sapply(filelist, read.table, header = F, simplify = FALSE)
         
           for (ii in 1:length(CHARM[,1])){   
             indx <- grep(paste0("_",CHARM$Index[ii],"_"),filelist)
             colnames(dataLH[[indx]]) <- CHARM$Abbreviation[ii]
           }
          
           dat.list <- bind_cols(dataLH)
           write.table(dat.list, paste0("E:/DREADDS/CHARM-SARM_ATLAS_SPACE/",mkey[mk],"/ALLBRAINCOR/","Frame_",mkey[mk],"_",session,"_",hemisph[hem],"_RUN",ran,".txt"), append = FALSE, sep = " ", dec = ".",  row.names = FALSE, col.names = TRUE)
          }
      }
    }
  }
               
}





```

## **DIRTY path to Matrices**

```{r homer, warning=FALSE, message = FALSE, echo=FALSE, fig.ncol = 2}
library(reshape2)
library(ggplot2)
library(Morpho)

setwd("E:/DREADDS/CHARM-SARM_ATLAS_SPACE/HOMER/ALLBRAINCOR/")
folder3 = "E:/DREADDS/CHARM-SARM_ATLAS_SPACE/HOMER/ALLBRAINCOR/"
filelistmatHo <- list.files(path=folder3, pattern=".txt", full.names = F) 
filelistmatHo <- as.list(filelistmatHo)

MAIN.HOL.mat <- array()
MAIN.HOR.mat <- array()


MAIN.HO <- data.frame()
session <- 2


for (hofile in seq(11, 80, by=10)){
  
  #------------Homer Session LH
  dat.Ho1 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho2 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+1]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho3 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+2]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho4 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+3]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho5 <- fisherz( cor(read.table(paste0(folder3,filelistmatHo[hofile+4]), header=TRUE),  use="all.obs", method="pearson"))
  
  my.list <- list(dat.Ho1, dat.Ho2, dat.Ho3, dat.Ho4, dat.Ho5)
  
  MAIN.HOL.mat <- cbind(MAIN.HOL.mat, array(my.list, dim= c(1,1,5))) #stack all matrices in one array
  
  listMeanLH <- apply(simplify2array(my.list), 1:2, mean)
  listsdLH <- apply(simplify2array(my.list), 1:2, sd)
  
  # reshape to transform into dataframe
  m_HOLH<-melt(listMeanLH)
  m_HOLH<-data.frame(m_HOLH[!is.na(m_HOLH[,3]),]) # get rid of the NA matrix entries
  m_HOLH$value_lab<-sprintf('%.2f',m_HOLH$value)
  m_HOLH$session <- session
  m_HOLH$hem <- "LH"
  
   #------------Homer Session RH
  dat.Ho1 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho2 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+5]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho3 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+6]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho4 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+7]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Ho5 <-  fisherz(cor(read.table(paste0(folder3,filelistmatHo[hofile+8]), header=TRUE),  use="all.obs", method="pearson"))
  
  my.list <- list(dat.Ho1, dat.Ho2, dat.Ho3, dat.Ho4, dat.Ho5)
  
    MAIN.HOR.mat <- cbind(MAIN.HOR.mat, array(my.list, dim= c(1,1,5))) #stack all matrices in one array
  
  listMeanRH <- apply(simplify2array(my.list), 1:2, mean)
  listsdRH <- apply(simplify2array(my.list), 1:2, sd)
  
  # reshape to transform into dataframe
  m_HORH<-melt(listMeanRH)
  m_HORH<-data.frame(m_HORH[!is.na(m_HORH[,3]),]) # get rid of the NA matrix entries
  m_HORH$value_lab<-sprintf('%.2f',m_HORH$value)
  m_HORH$session <- session
  m_HORH$hem <- "RH"
  
  
  MAIN.HO <- rbind(MAIN.HO, m_HOLH, m_HORH)
  session <- session + 1
  
}


MAIN.HO$injection <- MAIN.HO$session

#

for (i in 1:8){
MAIN.HO$injection[MAIN.HO$session==i ] <- as.factor(session_type$injection[session_type$monkey=="HOMER" & session_type$session==i])
}



MAIN.HO$injection <- as.factor(MAIN.HO$injection)
levels(MAIN.HO$injection) <- levels(session_type$injection)

MAIN.HO$period <- MAIN.HO$session
MAIN.HO$period[MAIN.HO$session<5] <- "pre"
MAIN.HO$period[MAIN.HO$session>4] <- "post"
MAIN.HO$period <- as.factor(MAIN.HO$period)


ggplot(subset(MAIN.HO, session >4), aes(Var2, Var1, fill = value, label=value_lab)) + 
  geom_tile() + 
  facet_wrap(hem~injection)+
  scale_fill_gradient2(low="blue",mid="white", high="red", midpoint = 0) +
  ggtitle("Homer - post-transfection sessions")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot( MAIN.HO , aes(value, fill=as.factor(injection))) + 
  geom_histogram(position="identity", binwidth=.05, alpha=.5) + 
  facet_wrap(period~hem)+
  scale_fill_manual(values=c("grey60","darkred")) +
  ggtitle("Homer - all  sessions")


ggplot(MAIN.HO, aes(Var2, Var1, fill = value, label=value_lab)) + 
  geom_tile() + 
  facet_wrap(period~hem*injection, nrow = 2)+
  scale_fill_gradient2(low="blue",mid="white", high="red", midpoint = 0) +
  ggtitle("Homer - all sessions")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# look at difference for session post chir  ATTENTION 11/9/2023 test without HOmer session 5 -post/control-
injecHO.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(MAIN.HO, session>5), mean) #ATTENTION 11/9/2023 test without HOmer session 5 -post/control-

#------------------HOMER
injecHO.mat.CONT<- subset(injecHO.mat, injection=="Control")
injecHO.mat.DCZ<- subset(injecHO.mat, injection=="DCZ")
injecHO.mat.diff <- injecHO.mat.DCZ
injecHO.mat.diff$value <- injecHO.mat.DCZ$value - injecHO.mat.CONT$value

ggplot(injecHO.mat.diff, aes(Var2, Var1, fill = value)) + 
  geom_tile() + 
  facet_wrap(hem~.)+
  scale_fill_gradient2(low="blue",mid="yellow", high="red", midpoint = 0, limits = c(-0.5, 0.5)) +
  ggtitle("Homer - post-transfection sessions DCZ-CONTROL")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



# look at difference for session pre chir
injecHOp.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(MAIN.HO, session<5), mean)

injecHOp.mat.CONT<- subset(injecHOp.mat, injection=="Control")
injecHOp.mat.DCZ<- subset(injecHOp.mat, injection=="DCZ")
injecHOp.mat.diff <- injecHOp.mat.DCZ
injecHOp.mat.diff$value <- injecHOp.mat.DCZ$value - injecHOp.mat.CONT$value

ggplot(injecHOp.mat.diff, aes(Var2, Var1, fill = value)) + 
  geom_tile() + 
  facet_wrap(hem~.)+
  scale_fill_gradient2(low="blue",mid="yellow", high="red", midpoint = 0, limits = c(-0.5, 0.5)) +
  ggtitle("Homer - pre-transfection sessions DCZ-CONTROL")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))




```

#DONUT
```{r donut, warning=FALSE, message = FALSE, echo=FALSE, fig.ncol = 2}
library(reshape2)
library(ggplot2)

setwd("E:/DREADDS/CHARM-SARM_ATLAS_SPACE/DONUT/ALLBRAINCOR/")
folder3 = "E:/DREADDS/CHARM-SARM_ATLAS_SPACE/DONUT/ALLBRAINCOR/"
filelistmatDo <- list.files(path=folder3, pattern=".txt", full.names = F) 
filelistmatDo <- as.list(filelistmatDo)


MAIN.DOL.mat <- array()
MAIN.DOR.mat <- array()

MAIN.DO <- data.frame()
session <- 1

for (Dofile in seq(1, 80, by=10)){
  
  #------------Do Session LH
  dat.Do1 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do2 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+1]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do3 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+2]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do4 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+3]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do5 <- fisherz( cor(read.table(paste0(folder3,filelistmatDo[Dofile+4]), header=TRUE),  use="all.obs", method="pearson"))
  
  my.list <- list(dat.Do1, dat.Do2, dat.Do3, dat.Do4, dat.Do5)
    MAIN.DOL.mat <- cbind(MAIN.DOL.mat, array(my.list, dim= c(1,1,5))) #stack all matrices in one array
  
  listMeanLH <- apply(simplify2array(my.list), 1:2, mean)
  listsdLH <- apply(simplify2array(my.list), 1:2, sd)
  
  # reshape to transform into dataframe
  m_DOLH<-melt(listMeanLH)
  m_DOLH<-data.frame(m_DOLH[!is.na(m_DOLH[,3]),]) # get rid of the NA matrix entries
  m_DOLH$value_lab<-sprintf('%.2f',m_DOLH$value)
  m_DOLH$session <- session
  m_DOLH$hem <- "LH"
  
   #------------Donut Session RH
  dat.Do1 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do2 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+5]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do3 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+6]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do4 <-  fisherz(cor(read.table(paste0(folder3,filelistmatDo[Dofile+7]), header=TRUE),  use="all.obs", method="pearson"))
  dat.Do5 <- fisherz( cor(read.table(paste0(folder3,filelistmatDo[Dofile+8]), header=TRUE),  use="all.obs", method="pearson"))
  
  my.list <- list(dat.Do1, dat.Do2, dat.Do3, dat.Do4, dat.Do5)
   MAIN.DOL.mat <- cbind(MAIN.DOL.mat, array(my.list, dim= c(1,1,5))) #stack all matrices in one array
   
  listMeanRH <- apply(simplify2array(my.list), 1:2, mean)
  listsdRH <- apply(simplify2array(my.list), 1:2, sd)
  
  # reshape to transform into dataframe
  m_DORH<-melt(listMeanRH)
  m_DORH<-data.frame(m_DORH[!is.na(m_DORH[,3]),]) # get rid of the NA matrix entries
  m_DORH$value_lab<-sprintf('%.2f',m_DORH$value)
  m_DORH$session <- session
  m_DORH$hem <- "RH"
  
  
  MAIN.DO <- rbind(MAIN.DO, m_DOLH, m_DORH)
  session <- session + 1
  
}


MAIN.DO$injection <- MAIN.DO$session

for (i in 1:8){
MAIN.DO$injection[MAIN.DO$session==i ] <- as.factor(session_type$injection[session_type$monkey=="DONUT" & session_type$session==i])
}
MAIN.DO$injection <- as.factor(MAIN.DO$injection)
levels(MAIN.DO$injection) <- levels(session_type$injection)

MAIN.DO$period <- MAIN.DO$session
MAIN.DO$period[MAIN.DO$session<5] <- "pre"
MAIN.DO$period[MAIN.DO$session>4] <- "post"
MAIN.DO$period <- as.factor(MAIN.DO$period)


ggplot(subset(MAIN.DO, session >4), aes(Var2, Var1, fill = value, label=value_lab)) + 
  geom_tile() + 
  facet_wrap(hem~injection)+
  scale_fill_gradient2(low="blue",mid="white", high="red", midpoint = 0) +
  ggtitle("Donut - post-transfection sessions")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot( MAIN.DO , aes(value, fill=as.factor(injection))) + 
  geom_histogram(position="identity", binwidth=.05, alpha=.5) + 
  facet_wrap(period~hem)+
  scale_fill_manual(values=c("grey60","darkred")) +
  ggtitle("Donut - all  sessions")



#--------------------DONUT

# look at difference for session pre chir
injecDOp.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(MAIN.DO, session<5), mean)

injecDOp.mat.CONT<- subset(injecDOp.mat, injection=="Control")
injecDOp.mat.DCZ<- subset(injecDOp.mat, injection=="DCZ")
injecDOp.mat.diff <- injecDOp.mat.DCZ
injecDOp.mat.diff$value <- injecDOp.mat.DCZ$value - injecDOp.mat.CONT$value

ggplot(injecDOp.mat.diff, aes(Var2, Var1, fill = value)) + 
  geom_tile() + 
  facet_wrap(hem~.)+
  scale_fill_gradient2(low="dodgerblue",mid="yellow", high="darkred", midpoint = 0, limits = c(-0.5, 0.5)) +
  ggtitle("Donut - pre-transfection sessions DCZ-CONTROL")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


# look at difference for session post chir
injecDO.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(MAIN.DO, session>4), mean)

injecDO.mat.CONT<- subset(injecDO.mat, injection=="Control")
injecDO.mat.DCZ<- subset(injecDO.mat, injection=="DCZ")
injecDO.mat.diff <- injecDO.mat.DCZ
injecDO.mat.diff$value <- injecDO.mat.DCZ$value - injecDO.mat.CONT$value

ggplot(injecDO.mat.diff, aes(Var2, Var1, fill = value)) + 
  geom_tile() + 
  facet_wrap(hem~.)+
  scale_fill_gradient2(low="blue",mid="yellow", high="red", midpoint = 0, limits = c(-0.5, 0.5)) +
  ggtitle("DONUT - post-transfection sessions DCZ-CONTROL")+
  theme(axis.text=element_text(size=5),axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```




#Identify regions

```{r regions, warning=FALSE, message = FALSE, echo=FALSE}

MAIN.HO$region1 <- fct_collapse( MAIN.HO$Var1, Frontal = CHARM$Abbreviation[1:50], Autre = CHARM$Abbreviation[51:133])

MAIN.HO$region2 <- fct_collapse( MAIN.HO$Var2, Frontal = CHARM$Abbreviation[1:50], Autre = CHARM$Abbreviation[51:133])

frontHO <- subset(MAIN.HO, region1=="Frontal" & region2=="Frontal")

injecFrontHO.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(frontHO, session>4), mean)
injecFrontHO.mat$Var1 <- as.character(injecFrontHO.mat$Var1)
injecFrontHO.mat$Var1 <- as.factor(injecFrontHO.mat$Var1)


injecFrontHO.mat$Var2 <- as.character(injecFrontHO.mat$Var2)
injecFrontHO.mat$Var2 <- as.factor(injecFrontHO.mat$Var2)


# DONUT
MAIN.DO$region1 <- fct_collapse( MAIN.DO$Var1, Frontal = CHARM$Abbreviation[1:50], Autre = CHARM$Abbreviation[51:133])

MAIN.DO$region2 <- fct_collapse( MAIN.DO$Var2, Frontal = CHARM$Abbreviation[1:50], Autre = CHARM$Abbreviation[51:133])

frontDO <- subset(MAIN.DO, region1=="Frontal" & region2=="Frontal")

injecFrontDO.mat <- aggregate(value ~ hem + injection + Var1 + Var2, data=subset(frontDO, session>4), mean)
injecFrontDO.mat$Var1 <- as.character(injecFrontDO.mat$Var1)
injecFrontDO.mat$Var1 <- as.factor(injecFrontDO.mat$Var1)


injecFrontDO.mat$Var2 <- as.character(injecFrontDO.mat$Var2)
injecFrontDO.mat$Var2 <- as.factor(injecFrontDO.mat$Var2)



```





#make Heatmaps
```{r heatm, warning=FALSE, message = FALSE, echo=FALSE}

make_a_map <- function(xx, titl){
  xxp <- as.matrix(xx)

  rd<-dist(xxp)
  rc<-hclust(rd)
  
  cd<-dist(t(xxp)) # transpose of xxp to have it in the good direction
  cc<-hclust(cd)

  par(cex.main=0.5)
  my_palette <- colorRampPalette(c("dodgerblue4", "white", "darkred"))(n = 150)
  heatmap.2(xxp, 
          Rowv=as.dendrogram(rc),
          Colv=as.dendrogram(cc),
          scale="column", 
          col= my_palette,
          main=titl,
          ylab="x", 
          xlab="y",
          cexCol=.6, cexRow = .6,
          na.rm=TRUE,
          trace="none")
  
}

## HOMER
#PRE CHIR
Hocontp <- xtabs(value ~ Var1 + Var2, subset(injecHOp.mat, hem =="RH" & injection == "Control" & value !=Inf))
make_a_map(Hocontp,"Homer RH Control - PRE")

Hoinjp <- xtabs(value ~ Var1 + Var2, subset(injecHOp.mat, hem =="RH" & injection == "DCZ" & value !=Inf))
make_a_map(Hoinjp,"Homer RH DCZ - PRE")


#POST CHIR
Hocont <- xtabs(value ~ Var1 + Var2, subset(injecHO.mat, hem =="RH" & injection == "Control" & value !=Inf))
make_a_map(Hocont,"Homer RH Control - POST")

Hoinj <- xtabs(value ~ Var1 + Var2, subset(injecHO.mat, hem =="RH" & injection == "DCZ" & value !=Inf))
make_a_map(Hoinj,"Homer LH DCZ - POST")

#frontal



HoFRcont <- xtabs(value ~ Var1 + Var2, subset(injecFrontHO.mat, hem =="RH" & injection == "Control" & value !=Inf))
make_a_map(HoFRcont,"Homer RH Control - POST")

HoFRinj <- xtabs(value ~ Var1 + Var2, subset(injecFrontHO.mat, hem =="RH" & injection == "DCZ" & value !=Inf))
make_a_map(HoFRinj,"Homer RH DCZ - POST")





# now lets order DCZ with the order of Control

 xxp <- as.matrix(HoFRcont)
  rd<-dist(xxp)
  rc<-hclust(rd)
  cd<-dist(t(xxp))
  cc<-hclust(cd)

 xxp2 <- as.matrix(HoFRinj)
titl = "Homer Frontal RH DCZ as Control - POST"
  
  par(cex.main=0.5)
  my_palette <- colorRampPalette(c("dodgerblue4", "white", "darkred"))(n = 150)
  heatmap.2(xxp2, 
          Rowv=as.dendrogram(rc),
          Colv=as.dendrogram(cc),
          scale="column", 
          col= my_palette,
          main=titl,
          ylab="x", 
          xlab="y",
          cexCol=.6, cexRow = .6,
          na.rm=TRUE,
          trace="none")
  
  
  dev.off()
  


## DONUT

#PRE CHIR
Docontp <- xtabs(value ~ Var1 + Var2, subset(injecDOp.mat, hem =="LH" & injection == "Control" & value !=Inf))
make_a_map(Docontp,"Donut LH Control - PRE")

Doinjp <- xtabs(value ~ Var1 + Var2, subset(injecDOp.mat, hem =="LH" & injection == "DCZ" & value !=Inf))
make_a_map(Doinjp,"Donut LH DCZ - PRE")


#POST CHIR
Docont <- xtabs(value ~ Var1 + Var2, subset(injecDO.mat, hem =="LH" & injection == "Control" & value !=Inf))
make_a_map(Docont,"Donut LH Control - POST")

Doinj <- xtabs(value ~ Var1 + Var2, subset(injecDO.mat, hem =="LH" & injection == "DCZ" & value !=Inf))
make_a_map(Doinj,"Donut LH DCZ - POST")

#frontal

DoFRcont <- xtabs(value ~ Var1 + Var2, subset(injecFrontDO.mat, hem =="LH" & injection == "Control" & value !=Inf))
make_a_map(DoFRcont,"Homer LH Control - POST")

DoFRinj <- xtabs(value ~ Var1 + Var2, subset(injecFrontDO.mat, hem =="LH" & injection == "DCZ" & value !=Inf))
make_a_map(DoFRinj,"Homer LH DCZ - POST")

# now lets order Frontal DCZ with the order of Control

 xxp <- as.matrix(DoFRcont)
  rd<-dist(xxp)
  rc<-hclust(rd)
  cd<-dist(t(xxp))
  cc<-hclust(cd)

 xxp2 <- as.matrix(DoFRinj)
titl = "DOnut LH DCZ as Control - POST"

diffxxp <- xxp2 - xxp
  
  par(cex.main=0.5)
  my_palette <- colorRampPalette(c("dodgerblue4", "white", "darkred"))(n = 150)
  heatmap.2(diffxxp, 
          Rowv=as.dendrogram(rc),
          Colv=as.dendrogram(cc),
          scale="column", 
          col= my_palette,
          main=titl,
          ylab="x", 
          xlab="y",
          cexCol=.6, cexRow = .6,
          na.rm=TRUE,
          trace="none")
  dev.off()
  
  
##----  

 # Create the dataframe to correlate Z control and z DCZ
  
  
VectData <- data.frame( "Z_control"=c(Docontp),"Z_DCZ"=  c(Doinjp), "ROI_cont"= cc$labels, "period"="pre", singe="Donut")

  VectData <- rbind(VectData, data.frame("Z_control"= c(Hocontp), "Z_DCZ"= c(Hoinjp), "ROI_cont"= cc$labels, "period"="pre", singe="Homer") )
  
VectData <- rbind(VectData,data.frame("Z_control"= c(Docont), "Z_DCZ"= c(Doinj), "ROI_cont"= cc$labels, "period"="post", singe="Donut") )


VectData <- rbind(VectData, data.frame("Z_control"= c(Hocont), "Z_DCZ"= c(Hoinj), "ROI_cont"= cc$labels, "period"="post", singe="Homer") )



#figures and stats
  ggplot(VectData, aes(x= Z_control, y= Z_DCZ, colour=period))+
    geom_point()+
    geom_smooth(method='lm', colour="blue")+
    facet_grid(singe~period)+
    scale_colour_manual(values=c("red","grey60"))+
    geom_hline(yintercept = 0)+ geom_vline(xintercept = 0)+
    geom_abline(intercept = 0, slope = 1, colour="blue",linetype = "dashed") +
    ggtitle("Matrix correlation per ROI of the CHARM atlas")
  
  
  mod.mat <- lm(Z_DCZ ~ Z_control * period, subset(VectData, singe== "Homer"))
  summary(mod.mat)
  
  mod.mat <- lm(Z_DCZ ~ Z_control * period, subset(VectData, singe== "Donut"))
  summary(mod.mat)
  
  
  ggplot(VectData, aes(x= Z_control, y= Z_DCZ))+
    geom_point(aes(colour=period), alpha=.1, size=2)+
    scale_colour_manual(values=c("red","grey40"))+
    facet_grid(. ~ singe)+
    geom_hline(yintercept = 0)+ geom_vline(xintercept = 0)+
    geom_abline(intercept = 0, slope = 1, colour="blue",linetype = "dashed") +
    ggtitle("Matrix correlation per ROI of the CHARM atlas")
  

  
```
  
#MATRIX CORRELATIONS 

One question is how the matrices of Z compare between pre and post surgery , because the graphs show big differences between pre and post in control especially for homer
  
  
  
```{r correl, warning=FALSE, message = FALSE, echo=FALSE}
# create a dataframe to correlate z before and after surgery
VectData2 <- data.frame( "Z_cont_pre"=c(Docontp),"Z_cont_post"=  c(Docont), "Z_DCZ_pre"=c(Doinjp),"Z_DCZ_post"=  c(Doinj), "ROI_cont"= cc$labels, singe="Donut")

VectData2 <- rbind(VectData2, data.frame( "Z_cont_pre"=c(Hocontp),"Z_cont_post"=  c(Hocont), "Z_DCZ_pre"=c(Hoinjp),"Z_DCZ_post"=  c(Hoinj), "ROI_cont"= cc$labels, singe="Homer") )
  
#figures and stats
  ggplot(VectData2, aes(x= Z_cont_pre, y= Z_cont_post, colour=singe))+
    geom_point()+
    geom_smooth(method='lm', colour="blue")+
    facet_grid(.~singe)+
    scale_colour_manual(values=c("grey40","grey60"))+
    geom_hline(yintercept = 0)+ geom_vline(xintercept = 0)+
    geom_abline(intercept = 0, slope = 1, colour="blue",linetype = "dashed") +
    ggtitle("Matrix correlation per ROI of the CHARM atlas")
  
    ggplot(VectData2, aes(x= Z_DCZ_pre, y= Z_DCZ_post, colour=singe))+
    geom_point()+
    geom_smooth(method='lm', colour="blue")+
    facet_grid(.~singe)+
    scale_colour_manual(values=c("brown3","brown4"))+
    geom_hline(yintercept = 0)+ geom_vline(xintercept = 0)+
    geom_abline(intercept = 0, slope = 1, colour="blue",linetype = "dashed") +
    ggtitle("Matrix correlation per ROI of the CHARM atlas")

    

    
    
    
a <- ggplot(VectData, aes(x= Z_control, fill=period))+
    geom_histogram(position="identity", aes(colour=period), alpha=.5, binwidth=.05)+
    scale_colour_manual(values=c("red","grey40"))+
    scale_fill_manual(values=c("red","grey40"))+
    facet_grid(. ~ singe)+
    scale_y_continuous(trans='log10') +
    geom_vline(xintercept = 0)+
    ggtitle("Matrix correlation per ROI of the CHARM atlas")
  
b   <- ggplot(VectData, aes(x= Z_DCZ, fill=period))+
    geom_histogram(position="identity", aes(colour=period), alpha=.5, binwidth=.05)+
    scale_colour_manual(values=c("red","grey40"))+
    scale_fill_manual(values=c("red","grey40"))+
    facet_grid(. ~ singe)+
  scale_y_continuous(trans='log10') +
    geom_vline(xintercept = 0)+
    ggtitle("Matrix correlation per ROI of the CHARM atlas")



  
  
```


There is apparently an effect of period pre/post on the entire data when we look at the change between DCZ versus control.

THe first conclusion is that we can't compare pre and post data.

Par ailleurs, il semble y avoir un artefact avec les session Homer post-control. Ceci est vérifiable dans le script CMArMonkey_DREADDS_HD_V4.rmd. La session 5 de Ho est avec une variance exceptionnellement faible comparée à toutes les autres sessions tous singes confondus.

Let's try the previous correlations without session 5 _Ho









We want to test whether the slopes of correlations between matrices reveal an effect of pre post on correlation and an effect of DCZ in post and pre separately 

```{r slops, warning=FALSE, message = FALSE, echo=FALSE}


 ##TO BE DONE: test if slopes are diff from 1 to check whether the DCZ vs Sham are similar or not in terms of correlation values [this is one way to compare the maps]
  #test mostly by calculating the slope and the standard error of the slope.
# Then you must calculate a t value as follow t = b1-b2/Sb1-Sb2 where b1 is the value of slope 1 (in your case your example: 0.81) and b2 is the value of slope 2 (in your case your example: 1) and Sb1 is the standard error of slope 1 and Sb2 is the standard error of slope 2 (in this case is 0 because a slope b=1 has zero standard error). In this way you calculate a t value and then you compared it with a t value from a t table with n-2 df and alfa 0.05 or 0.01, if t calculated is less than t value from the table, you can assume that the calculated slope is not different from 1. See Zar (1999). I think that first you must understant the principles of that analyses before you run it in a statistical package. 

# let's try to answer the question: is the entire matrix correlation between DCZ and Control in post for each monkey different from corr with slope = 1 ?

do.lm <- summary(lm(Z_DCZ~ Z_control, data= subset(VectData, singe=="Donut" & period=="pre")))
 
slop.do.lm = do.lm$coefficients[2,1]  
stdslop.do.lm = do.lm$coefficients[2,2]


t = (slop.do.lm - 1) / (stdslop.do.lm - 0)  

qt(0.01, 17689-2, lower.tail=FALSE)


do.lm.post <- summary(lm(Z_DCZ~ Z_control, data= subset(VectData, singe=="Donut" & period=="post")))
 
slop.do.lm.post = do.lm.post$coefficients[2,1]  
stdslop.do.lm.post = do.lm.post$coefficients[2,2]


t.post = (slop.do.lm.post - 1) / (stdslop.do.lm.post - 0)  


Ho.lm.post <- summary(lm(Z_DCZ~ Z_control, data= subset(VectData, singe=="Homer" & period=="post")))
 
slop.ho.lm.post = Ho.lm.post$coefficients[2,1]  
stdslop.ho.lm.post = Ho.lm.post$coefficients[2,2]


t.h.post = (slop.ho.lm.post - 1) / (stdslop.ho.lm.post - 0)  

Ho.lm.DCZ <- summary(lm(Z_DCZ_post~ Z_DCZ_pre, data= subset(VectData2, singe=="Homer")))
 
slop.ho.lm.DCZ = Ho.lm.DCZ$coefficients[2,1]  
stdslop.ho.lm.DCZ = Ho.lm.DCZ$coefficients[2,2]


t.h.DCZ = (slop.ho.lm.DCZ - 1) / (stdslop.ho.lm.DCZ - 0)  


```

Toute les slope sont differentes de 1. DE fait le grande nombre de valeurs renforce fortement la sensibilité.




## Concluding remarks:

*








